### 2015-12-02 paper.tex
Move sensor references comment to issue #23

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells \textbf{\textit{[need reference for each sensor - load cells, ADV, etc.]}}. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted, mounted at a fixed distance from the servo
motor, provides a redundant measurement. Turbine shaft angle was measured using
the servo drive's emulated encoder output, set to $10^5$ counts per turbine
shaft revolution. Carriage speed, and therefore inflow velocity was measured
using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed \textbf{\textit{[need to say how well the agreement between these two measurements are and which one is used throughout the paper; else, remove one of these]}} turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

>>>>

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted, mounted at a fixed distance from the servo
motor, provides a redundant measurement. Turbine shaft angle was measured using
the servo drive's emulated encoder output, set to $10^5$ counts per turbine
shaft revolution. Carriage speed, and therefore inflow velocity was measured
using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed \textbf{\textit{[need to say how well the agreement between these two measurements are and which one is used throughout the paper; else, remove one of these]}} turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
